Stack Safety is a Security Property

### 2021-04-10 tex/main.tex
Couple of comments
Responded to some abstract comments

We propose a formal criterion for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's stack frame''). These combine with a straightforward
well-bracketedness condition on the program's control flow that ensures that
callers and callees remain meaningfully distinct.\bcp{I am still not clear
  how well-bracketedness fits into the story.  (For me, it is the bracketing
  that {\em defines} where calls and returns happen, so there is something
  tautological about saying that `` well-bracketedness condition ensures
  that callers and callees remain meaningfully distinct''!)}

Our criterion is inspired by hardware tagging mechanisms for stack
protection, in particular the stack-safety ``micro-policies''
of~\citet{DBLP:conf/sp/RoesslerD18}, but its core reflects general
principles of stack safety\bcp{I wish we did not have to be so apologetic
  about being tied to micro-policies (and it is still not clear to me that
  we have to be... do we have a clear statement someplace of why our
  definition would not apply to CFI, for example? This seems like a critical
  discussion...)}. We define additional properties tailored for specific
contexts: a stronger property amenable to efficient testing and a weaker one
that is approximated by more efficient, lazy policies.

\bcp{... and now a sentence on testing!}

@@

%% %\begin{figure}[b]
%% %    \begin{minipage}{.4\textwidth}
%% %\begin{verbatim}
%% %int main() {
%% %  int x = 42;
%% %  f();
%% %  print(x);
%% %}
%% %\end{verbatim}
%% %    \end{minipage}
%% %    \begin{minipage}{.4\textwidth}
%% %\begin{verbatim}
%% %int main() {
%% %  int x = 1;
%% %  f();
%% %  if(x)
%% %    g();
%% %  else
%% %    h();
%% %}
%% %\end{verbatim}
%% %    \end{minipage}
%% %  \caption{Simple Examples}
%% %  \label{fig:examples1}
%% %\end{figure}

%% %\begin{figure}[b]
%% %    \begin{minipage}{.4\textwidth}
%% %\begin{verbatim}
%% %int main(int arg) {
%% %  if(arg)
%% %    g();
%% %  else
%% %    h();
%% %  f();
%% %}
%% %\end{verbatim}
%% %    \end{minipage}
%% %    \begin{minipage}{.4\textwidth}
%% %\begin{verbatim}
%% %int main() {
%% %  int x = 1;
%% %  f();
%% %  x = -x;
%% %  f();
%% %  print(x);
%% %}
%% %\end{verbatim}
%% %  \end{minipage}
%% %
%% %  \caption{More Examples}
%% %  \label{fig:examples2}
%% %\end{figure}

>>>>

We propose a formal criterion for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's state''). These are defined in terms of a control flow model
in which callees are meaningfully distinct from their callers due to being
bracketed by calls and returns. We further apply a straightforward notion of
``well-bracketed control flow'' that ensures that callers' control flow
can continue predictably after the return.

  \bcp{I am still not clear
  how well-bracketedness fits into the story.  (For me, it is the bracketing
  that {\em defines} where calls and returns happen, so there is something
  tautological about saying that `` well-bracketedness condition ensures
  that callers and callees remain meaningfully distinct''!)}
  \sna{Attempted to resolve this, it may need some work.}

Our criterion is inspired by hardware tagging mechanisms for stack
protection, in particular the stack-safety ``micro-policies''
of~\citet{DBLP:conf/sp/RoesslerD18}, but its core reflects general
principles of stack safety\bcp{I wish we did not have to be so apologetic
  about being tied to micro-policies (and it is still not clear to me that
  we have to be... do we have a clear statement someplace of why our
  definition would not apply to CFI, for example? This seems like a critical
  discussion...)}. Finally, we show that micro-policies do indeed enforce
our properties using property-based randomized testing. An eager micropolicy
that catches violations immediately enforces our stronger property, and we
define a weaker, more extensional form of the property that is enforced
by a ``lazy'' micropolicy -- one that, for performance reasons, may permit
local violations as long as they do not influence future behavior.

@@
